\documentclass[11pt,letterpaper]{article}
\pagestyle{empty}
\usepackage[top=1.0cm, bottom=0.5cm, left=1.0cm, right=1.0cm]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\renewcommand\familydefault{\sfdefault}

% ---- Colors ----
\definecolor{accent}{HTML}{0A66C2}

% ---- Section styling ----
\titleformat{\section}{\Large\bfseries\color{accent}}{}{0em}{}[\titlerule]

% ---- List spacing ----
\setlist[itemize]{leftmargin=1.2em, itemsep=1pt, topsep=1pt, parsep=0pt, partopsep=0pt}

\begin{document}

% ---- Header ----
{\Huge \bfseries Nabheet Singh Sandhu} \\[4pt]
\href{mailto:nabheet@berkeley.edu}{nabheet@berkeley.edu} \; | \;
(510) 364\textendash{}1386 \; |\;
Denver Metro Area \;|\;
\href{https://linkedin.com/in/nabheet}{linkedin.com/in/nabheet} \;|\;
\href{https://github.com/nabheet}{github.com/nabheet}

% ---- Summary ----
\section*{Summary}
Backend engineer and systems architect with 20+ years of experience in building distributed, cloud\textendash{}native applications. Known for driving performance improvements, enhancing observability, and leading teams to deliver secure and resilient infrastructure. Strong expertise across AWS, GCP, Kubernetes, and developer productivity tools.

% ---- Skills ----
\section*{Skills}
\textbf{Languages (in skill order):} Python, JavaScript, Node.js, Ruby, TypeScript \\
\textbf{Cloud Platforms:} AWS (EKS, EC2, Lambda, RDS, WAF), GCP (Cloud Run, SQL, Pub/Sub, Armor, Vertex AI), Pulumi \\
\textbf{DevOps \& Infra:} Kubernetes, Docker, Ansible, Jenkins, GitHub Actions, ELK Stack, Grafana, OpenTelemetry \\
\textbf{Databases:} PostgreSQL, MySQL, Redis, MongoDB \\
\textbf{Other:} Observability, CI/CD, TDD, Mentorship, Agile/Scrum \\
\textbf{Courses:} \href{https://www.udemy.com/certificate/UC-139cb69e-ff24-4de2-8889-df32f999fa21/}{AI Engineer Bootcamp},
                  \href{https://www.udemy.com/certificate/UC-835d16d0-903f-4afd-8f66-6d6da2ff75c3/}{AI Agent Engineer Course}, 
                  \href{https://coursera.org/share/1613a5d165fbe645bb55de4eed96ce8b}{Machine Learning}

% ---- Experience ----
\section*{Experience}

\textbf{Software Engineer IV (Contract)} \hfill Spectrum \hfill March, 2026\textendash{}Current
\begin{itemize}
  \item Building Artificial Intelligence (SpectrumGPT) tools to assist with various internal business processes and workflows.
\end{itemize}

\textbf{Sr Software Engineer (Contract)} \hfill CoBank \hfill December, 2025\textendash{}March, 2026
\begin{itemize}
  \item Initiating member of new development team responsible for setup and definition of project architecture and workflows for new lending product with the goal of migration from on-prem datacenter to AWS\@.
  \item Improved onboarding process for new engineers by creating documentation and walkthroughs for various development and deployment processes.
\end{itemize}

\textbf{Sr Software Engineer} \hfill Functional Finance \hfill September, 2023\textendash{}October, 2025
\begin{itemize}
  \item Implemented Artificial Intelligence (AI) agents for auto\textendash{}generation of QA test cases reducing QA testing time during every release cycle using Google\textquoteright{}s Agent Development Kit (ADK) and Vertex AI.\@
  \item Architected OpenTelemetry implementation to provide tracing and metrics across various tiers of the product. Providing valuable insights and debugging abilities to resolve performance and various deadlock issues.
  \item Implemented VS Code Dev Containers based development environment to reduce engineer onboarding times, improve efficiency and provide consistent experience.
  \item Implemented various Google Compute Platform (GCP) features to host and protect Python and NodeJS based APIs. This involved Cloud Run Services/Jobs/Functions, Cloud Armor, Cloud Load Balancer, Cloud SQL, Pub/Sub and others.
  \item Optimized Python FastAPI container startup in GCP Cloud Run to reduce average API startup times by almost 50\%.
  \item Optimized Docker image builds and deployments by reducing image size and build times.
  \item Implemented various business features in Python using various tools like FastAPI, Hypercorn, SQLAlchemy, PostgreSQL, RQ, etc.
  \item Implemented a PDF generation service using NodeJS, Puppeteer and Chromium on GCP Cloud Run.
  \item Resolved various issues caused by incorrect Python implementation manifesting as infrastructure issues such as creating unlimited HTTPX clients causing all source ports to be consumed on system.
  \item Implemented minor UI features in NodeJS and React.
  \item Lead a team of 2 other engineers to accomplish various business goals.
\end{itemize}

\textbf{Software Engineer V} \hfill GoDaddy \hfill April, 2021\textendash{}September, 2023
\begin{itemize}
  \item Architected and implemented Cloud Linux 8 based Shared Hosting product to replace the current product which is based on Cloud Linux 6.
  \item Optimized performance of Shared Hosting product components\textendash{}Apache Web Server, MySQL, Exim and various other Linux components across 1.5 million customer accounts.
  \item Reduced page load time of Shared Hosting customer websites by 50\%.
  \item Researched and replaced Apache MPM Event to improve performance by 2x over MPM Worker on Shared Hosting environment.
  \item Discovered \href{https://github.com/icing/mod_h2/issues/212\#issuecomment-954906013}{bug} in Apache Web Server HTTP2 implementation.
  \item Discovered bug in Apache Web Server where large htaccess files cause Apache memory to grow unbounded and eventually cause performance issues. Resolved by automatically removing certain tags from customer htaccess files.
  \item Architected and implemented Ansible AWX on Elastic Kubernetes Service on Amazon Web Services which enabled SRE to reduce Shared Hosting environment patching times from more than 30 days to less than 7 days.
  \item Improved development process by incorporating VS Code Remote containers.
  \item Improved filesystem performance of CentOS6 based product by changing IO Scheduler.
  \item Improved enterprise authentication to Shared Hosting servers by writing a python script that uses YubiKey for 2FA with Okta to download client SSH keys.
  \item Implemented Jupyter notebook to prove that TCP connect times from Shared Hosting DC to various regions do not correspond to distance.
  \item Experimented and developed two different server performance models, first by using PCA to reduce dimensions of server metrics data and second by using a simple weighted sum of the metrics data so servers could be ordered by performance quality.
  \item Implemented linear regression model to prove that Server Response Time was not statistically related to server load.
\end{itemize}

\textbf{Software Engineer IV} \hfill GoDaddy \hfill August, 2015\textendash{}April, 2021
\begin{itemize}
  \item Architected and designed WAF/CDN 2.0 product on Amazon Web Services.
  \item Architected and implemented on\textendash{}prem Kubernetes on OpenStack for Shared Hosting provisioning system.
  \item Reduced customer downtime by optimizing call\textendash{}center agent recovery of Customer Virtual Machines after kernel panics and other patching related issues.
  \item Introduced enhanced product security by using signed SSH keys.
  \item Developed features for three different products \textendash{} Virtual Private Server, Business Hosting and Shared Hosting.
  \item Optimized Ruby on Rails code and SQL queries.
  \item Introduced process changes utilizing Jenkins, Ansible and Docker.
  \item Conducted knowledge sharing lunch \& learn sessions on various topics.
  \item Presented on log aggregation and analysis at GoDaddy Company TechFest.
  \item Mentored Junior developers.
\end{itemize}

\textbf{Sr. Software Engineer/Architect} \hfill FSW, GoDaddy, Visa, Qwest \hfill February, 2003\textendash{}July, 2014
\begin{itemize}
  \item Architected an enterprise scale ELK (Elasticsearch, Logstash and Kibana) stack for aggregating application, system and network device logs, enabling real\textendash{}time metrics collection, visualization and analysis. This reduced response times for detecting and resolving application issues. Also created Kibana dashboards for providing insights into usage for each application and performance such as avg/min/max UI response time, product search term metrics, browser usage statistics, response times by URI, requests per second, etc. This system is collecting and indexing about 30GB per day.
  \item Worked on various projects including building highly available payment processing systems at Visa, building large scale telecom billing systems at Qwest and building various eCommerce systems at GoDaddy.
  \item Provided technical leadership and coaching to development teams on industry best practices.
\end{itemize}

% ---- Education ----
\section*{Education}
\textbf{University of California, Berkeley} \hfill B.S. Electrical Engineering \& Computer Science, 2002

% ---- Accomplishments ----
\textbf{Accomplishments}
\begin{itemize}
  \item Selected to be a part of a Tiger team to improve performance of Shared Hosting product.
  \item Provisional patent filed by Visa.
  \item Dean\textquoteright{}s List: 8 semesters.
  \item Fifth engineer to join startup at Functional Finance.
\end{itemize}

\end{document}
